---
title: "Plot SNP frequencies headmap"
author: "zeroliu"
date: "2024-10-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

This is an example Rmarkdown file to plot heatmap of SNP frequencies.

The input SNP frequencies file is a `tsv` format file, _i.e._, columns/fields delimited by a "\t".

Example of input file:

```
	P13L	D63G	R123A	G202R	P377K
TypeA	0	1.0000	0.9230	0	0.2345
TypeB	1.0000	1.0000	0	0.4583	0.8023
TypeC	1.0000	0.5824	0.9872	1.0000	0.3345
```

SNP frequencies could be fetched from the output of the script `snp_freq.pl` in the last column `Freq`.

Please note:

- Replace `NA` in `Freq` column with `0`.

Load necessary libraries:

```{r}
library(dplyr)
library(pheatmap)
library(readr)
library(tidyr)
```

Working dir: `getwd()`.

Then plot headmap:

### Read file:

```{r}
fin = "input_freq.tsv"

data <- read.table(fin, header = TRUE, row.names = 1, sep = "\t")
```

### Plotting heatmap

Please change options to fit your requirements:

- Modify `color` for different color or color gradients.
- Midify `cellwidth` and `cellheight` for different square size, in `points`.

```{r}
p <- pheatmap(data,
              cluster_rows = FALSE, 
              cluster_cols = FALSE,
              color = colorRampPalette(c("white", "purple4"))(100),
              cellwidth = 12,
              cellheight = 12)
```

### Output to PDF format file

```{r}
pdf("heatmap.pdf", paper = "a4")
p
dev.off()
```

# DONE

